---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
options(width = 100)
```

# Impact of Model Misspecification in Shared Frailty Survival Models

This repository contains the code required to simulate data, fit each model, and produce summary tables and figures for the manuscript titled _Impact of model misspecification in shared frailty survival models_ by Gasparini et al. In addition to that, this repository contains the Supporting Web Material and a dataset with the full results of the simulation study.

A preprint of the manuscript is available on [arXiv](https://arxiv.org/abs/1810.08140); please get in touch via [Twitter](https://twitter.com/ellessenne) or [e-mail](mailto:ag475@leicester.ac.uk?subject=Preprint: Impact of Model Misspecification in Shared Frailty Survival Models) if you have any comment.

The following files are included in this repository:

* `make_data_dgms.R`, an R script file used to simulate the data under each data-generating mechanism;
* `make_models.R`, an R script file used to fit the models;
* `make_summaries.R`, an R script file used to aggregate the results and obtain summary statistics for each model and data-generating mechanism;
* `results-nn.RDS`, `nn` serialised R objects containing the raw results of the simulation study. See the next chapter for information on how to combine them;
* `summary.RDS`, a serialised R object containing the summary statistics for each model and data-generating mechanism. `summary.RDS` was produced by `make_summaries.R`;
* `suppl.pdf`, a PDF document with the Supporting Web Material.

### Splitting/Combining Results

In order to upload the full results of the simulation study, we had to split them in chunks as the single file `Results.RDS` was too large to upload on GitHub. In this section, we illustrate how the file was split in chunks and how to re-combine them if needed.

We first imported the single file with results, too large to store on GitHub:

```{r}
# done <- lapply(list.files("Results", pattern = "^out_|^multiout_", full.names = TRUE), readRDS)
# saveRDS(done, "Results.RDS")
done <- readRDS("Results.RDS")
```

As `done` is a list of `data.frame` objects, we combined it into a single `data.frame`:

```{r}
library(dplyr)
done <- dplyr::bind_rows(done)
```

We then split the single `data.frame` into chunks of roughly equal size:

```{r}
results.01 <- done[1:ceiling(nrow(done) / 10), ]
results.02 <- done[(ceiling(nrow(done) / 10) + 1):ceiling(nrow(done) / 10 * 2), ]
results.03 <- done[(ceiling(nrow(done) / 10 * 2) + 1):ceiling(nrow(done) / 10 * 3), ]
results.04 <- done[(ceiling(nrow(done) / 10 * 3) + 1):ceiling(nrow(done) / 10 * 4), ]
results.05 <- done[(ceiling(nrow(done) / 10 * 4) + 1):ceiling(nrow(done) / 10 * 5), ]
results.06 <- done[(ceiling(nrow(done) / 10 * 5) + 1):ceiling(nrow(done) / 10 * 6), ]
results.07 <- done[(ceiling(nrow(done) / 10 * 6) + 1):ceiling(nrow(done) / 10 * 7), ]
results.08 <- done[(ceiling(nrow(done) / 10 * 7) + 1):ceiling(nrow(done) / 10 * 8), ]
results.09 <- done[(ceiling(nrow(done) / 10 * 8) + 1):ceiling(nrow(done) / 10 * 9), ]
results.10 <- done[(ceiling(nrow(done) / 10 * 9) + 1):nrow(done), ]
```

We test that by re-combining the chunks we obtain the same `data.frame`:

```{r}
done.c <- dplyr::bind_rows(
  results.01,
  results.02,
  results.03,
  results.04,
  results.05,
  results.06,
  results.07,
  results.08,
  results.09,
  results.10
)
all.equal(current = done.c, target = done)
```

If the previous test passed, we export each chunk as a separate `.RDS` file:

```{r}
if (all.equal(current = done.c, target = done)) {
  saveRDS(results.01, file = "results-01.RDS")
  saveRDS(results.02, file = "results-02.RDS")
  saveRDS(results.03, file = "results-03.RDS")
  saveRDS(results.04, file = "results-04.RDS")
  saveRDS(results.05, file = "results-05.RDS")
  saveRDS(results.06, file = "results-06.RDS")
  saveRDS(results.07, file = "results-07.RDS")
  saveRDS(results.08, file = "results-08.RDS")
  saveRDS(results.09, file = "results-09.RDS")
  saveRDS(results.10, file = "results-10.RDS")
}
```

To recombine the chunks uploaded on GitHub, first download all the files in a single directory. Then, run the following `R` code making sure that the working directory is the directory where the files are saved:

```{r}
done.r <- lapply(1:10, function(n) readRDS(file = paste0("results-", sprintf("%02d", n), ".RDS")))
done.r <- do.call(rbind.data.frame, done.r)
```

Test that we obtain the same results:

```{r}
all.equal(current = done.r, target = done)
```
